Exploratory analysis of context: Examples

### 2021-11-29 analysis/exploratory/context_versus_nocontext/rscripts/examples.Rmd
updated talk for linguae

# Relative difference between Context and NoContext Experiments

## For A-paraphrase

```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "a") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = context-nocontext) %>% 
  # arrange in descending order to see the high positive difference
  arrange(desc(difference)) 
```

### High Positive Difference

Examples for which the mean rating for 'a' was higher in the Context experiment than in the NoContext experiment.

1. The first biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

2. The second biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

3. The third biggest.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

4. The fourth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

5. The fifth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

### High Negative Difference
Examples for which the mean rating for 'a' was higher in the NoContext experiment than in the Context experiment.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "a") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = context-nocontext) %>% 
  # arrange in ascending order to see the high negative difference
  arrange(difference) 
```

1. The first biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

2. The second biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

3. The third biggest.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

4. The fourth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

5. The fifth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

## For Every-paraphrase

```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "every") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = context-nocontext) %>% 
  # arrange in descending order to see the high positive difference
  arrange(desc(difference)) 
```

### High Positive Difference

Examples for which the mean rating for 'a' was higher in the Context experiment than in the NoContext experiment.

1. The first biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

2. The second biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

3. The third biggest.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

4. The fourth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

5. The fifth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

### High Negative Difference
Examples for which the mean rating for 'a' was higher in the NoContext experiment than in the Context experiment.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "every") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = context-nocontext) %>% 
  # arrange in ascending order to see the high negative difference
  arrange(difference) 
```

1. The first biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

2. The second biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

3. The third biggest.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

4. The fourth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

5. The fifth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

## For The-paraphrase

```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "the") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = context-nocontext) %>% 
  # arrange in descending order to see the high positive difference
  arrange(desc(difference)) 
```

### High Positive Difference

Examples for which the mean rating for 'a' was higher in the Context experiment than in the NoContext experiment.

1. The first biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

2. The second biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

3. The third biggest.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

4. The fourth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

5. The fifth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

### High Negative Difference
Examples for which the mean rating for 'a' was higher in the NoContext experiment than in the Context experiment.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "the") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = context-nocontext) %>% 
  # arrange in ascending order to see the high negative difference
  arrange(difference) 
```

1. The first biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

2. The second biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

3. The third biggest.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

4. The fourth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

5. The fifth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

# Examples with the smallest difference between the two tasks

```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "a") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = abs(context-nocontext)) %>% 
  arrange(difference) 
```

1. The first smallest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

2. The second smallest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

3. The third smallest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

4. The fourth smallest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

5. The fifth smallest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

# Look at absolute differences between Context and NoContext

Ignoring the directionality of the difference, let's see which examples 
change the most between the two tasks.

## First for A-Paraphrase
```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "a") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = abs(context-nocontext)) %>% 
  arrange(desc(difference)) 
```

1. The first biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

2. The second biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

3. The third biggest.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

4. The fourth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

5. The fifth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

>>>>

Interesting MA with domain restriction

```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == "2512:34") %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == "2512:34") %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == "2512:34") %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

World knowledge
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == "101503:16") %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == "101503:16") %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == "101503:16") %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

MS

```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == "38489:4") %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == "38489:4") %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == "38489:4") %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

hmmm
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == "11532:7") %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == "11532:7") %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == "39551:19") %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```
